Assignment 5

### 2015-02-23 rmtw/a5/latex8.tex
Research question added
Added notes for problem statement

\title{Assignment 4}

@@

\SubSection{Statement of the Problem}

@@

\SubSection{Research Question(s)}
One clear main research question
Sub qs

@@

\begin{itemize}
\item Describe and explain the research strategy (i.e. SLR) and investigation methods that will be used for the study. 
\item Motivate your choice of experiment using relevant references. 
\item Search string including keywords and used databases
\item inclusion/exlusion criteria
\item data extraction
\item data synthesis
\item quality assessment
\end{itemize}

@@

\textbf{Planning the review}
\begin{itemize}
\item Identification of the need for a review (5.1)
Check other SLRs in the field and evaluate them
\item Commissioning a review (5.2)
not needed
\item Specifying the research question(s) (5.3)
this is very impoirtant :)
the search process must identify primary studies htat address the research questions
the data extraction proccess must extract the data items needed to answer the questions
the data analysis process must synthesise the data in such a way that the questions cna b eansewrd.

>>>>

\title{Assignment 5}

@@

\SubSection{Statement of the Problem}
Companies don't know if adopting MDD will be beneficial in terms of money and improved software quality.

@@

\SubSection{Research Question(s)}
One clear main research question
RQ 1 - In which situations should companies expect MDD to be successfully adopted?

@@

\begin{itemize}
\item Describe and explain the research strategy (i.e. SLR) and investigation methods that will be used for the study. 
\item Motivate your choice of experiment using relevant references. 
\item Search string including keywords and used databases
\item inclusion/exclusion criteria
\item data extraction
\item data synthesis
\item quality assessment
\end{itemize}

@@

\textbf{Planning the review}
\begin{itemize}
\item Identification of the need for a review (5.1)
Check other SLRs in the field and evaluate them
\item Commissioning a review (5.2)
not needed
\item Specifying the research question(s) (5.3)
this is very important :)
the search process must identify primary studies that address the research questions
the data extraction process must extract the data items needed to answer the questions
the data analysis process must synthesise the data in such a way that the questions can be answered.
